---
title: "AssignmentPart1"
author: "ucesday"
date: "27 October 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
# Assignment Part 1


## Introduction

Intro about GIS 

The purpose of this work is to have created two maps using different GIS and graphics software programs.  One using a GUI software (here ArcGIS has been used), and a programming based software (here R based map has been created using Rstudio), and to provide a critique of the methods used.

(Maybe a review of the task is a waste of word count, but some intro useufl, maybe more bullet point like)



## Libraries 
```{r, echo=FALSE}
#libraries set to hidden for now - remember to remove heading if not shown
library(knitr)
library(colorspace)
library(ggplot2)
library(png)
```


## ArcMap Map
wfh excluded


```{r, echo=FALSE}  
img1_path <- "C:/Users/pippa/OneDrive/Documents/GitHub/CASA-GIS-T1/Arc_MTW_IOW1.png"
##sort out sizing some other time. 
##if knitting to html the graphics are going to have to be smaller maybe with retina setting
include_graphics(img1_path)
```

```{r 2}

##{r, fig.width=2}out.width = "25%"
## https://www.zevross.com/blog/2017/06/19/tips-and-tricks-for-working-with-images-and-figures-in-r-markdown-documents/
```



This is a map using ArcGIS.

Data from: <>,<>,<>. Insert hyperlinks... how to have an alt text appear to hyperlink?



When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
